% !TeX spellcheck = en_GB
% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[a4paper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Set your name here
\def\name{Matthew Lake}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  allcolors = black,
  pdfauthor = {\name},
  pdfkeywords = {resume, software engineering, mathematics, arts},
  pdftitle = {Matthew Lake: Resume},
  pdfsubject = {Matthew Lake: Resume},
  pdfpagemode = UseNone
}

% Set margins and spacing
\geometry{
	tmargin = 0.7cm,
	bmargin = 0.7cm,
	lmargin = 3.25cm,
	rmargin = 2.5cm
}
\renewcommand{\baselinestretch}{0.9} 
\usepackage{titlesec}
\titlespacing*{\section}
{-30pt}{0pt}{1ex}

% Remove page numbering
\pagenumbering{gobble}

% Prevent hyphenation
\hyphenpenalty = 500
\raggedright

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}
\usepackage{enumitem}
\newlength{\jeroenlen}

% Template for resume items
\newcommand{\dateitem}[1] {\item[\textbf{#1 :}]}
\newcommand{\resumesection}[1]{\section*{\accentcolour #1}}
\newcommand{\resumeitem}[4]{
	\dateitem{#1} {\textbf{#2,} \textit{#3}
		
		#4
	}	
}

% Use sans-serif font
\renewcommand{\familydefault}{\sfdefault}

% Nice icons and colours
\usepackage[dvipsnames]{xcolor}
\newcommand{\accentcolour}{\color{NavyBlue}}
\usepackage{fontawesome}

\begin{document}
\centerline{\rmfamily \accentcolour \Huge \bfseries \name}
\vspace{-0.5\baselineskip}

\begin{center}
	\begin{tabular}{c  c c c}
		{\color{NavyBlue}\faPhone\space} 0419 747 426 & 
		{\color{NavyBlue}\faEnvelope\space} \href{mailto:mgtlake@outlook.com}{mgtlake@outlook.com} & 
		{\color{NavyBlue}\faGithub\space} \href{https://github.com/mgtlake}{github.com/mgtlake} & 
		{\color{NavyBlue}\faLinkedinSquare\space} \href{https://linkedin.com/in/mgtlake}{linkedin.com/in/mgtlake}
	\end{tabular}
\end{center}

\resumesection{Education}
\begin{itemize}[itemsep=0pt]
	\dateitem{2014 -- 2019} {\textbf{Bachelor of Engineering (Software) \&
			Bachelor of Arts (History, Mathematics)}
		
		University of Queensland, GPA: 6.49 / 7
		
		
		
		% TODO is this the right place to mention?
		% \dateitem{Coursework} Machine Learning, Compilers \& Interpreters, High Performance Computing, 
		\dateitem{2019} UQ Computing Society management committee member.
		\dateitem{2017} Studied abroad at University College London on a UQ Exchange Scholarship.
	}
\end{itemize}

%	, connecting to an internal process visualisation service via AWS Kinesis

\resumesection{Experience}
\begin{itemize}
	\resumeitem{2018 -- 2019}{Amazon}{Software Development Engineer Intern}{
		Developed a library for API logging using \textbf{Spring Aspect-Orientated-Programming} and \textbf{Java} annotations. Built infrastructure to redact sensitive customer data, and designed blacklists adhering to internal Data Classification standards.
		
		Worked on a high-availability \textbf{Java Spring} backend service managing on-site fulfilment of Amazon Fresh pickup orders. Tuned the \textbf{DynamoDB} database to support 10x scaling.
		
%		Designed algorithms to locate an RFID tag in n-dimensional space for a prototype smart warehouse.
		Designed algorithms for non-linear spatial location of RFID tags for a prototype smart warehouse.
		
		Developed Chaos Engineering tools for \textbf{AWS Lambda}, using \textbf{Python} and \textbf{Node JS}.
		
		First place in two internal hackathons, and second place in an internal algorithms contest. % TODO is this relevent enough?
	}
	
	\resumeitem{2017 -- 2019}{University of Queensland}{Tutor}{	
		Prepared lessons, taught classes, and graded assessment. Student feedback rating of 4.86 / 5.
		
		\textit{CSSE2002 `Programming in the Large'} (3 Semesters)
		\begin{itemize}[noitemsep,topsep=0pt]
			\item[] Taught \textbf{OOP} design patterns, formal specifications, and intermediate \textbf{Java} programming.
		\end{itemize}		
		\textit{CSSE3100 `Reasoning About Programs'} (1 Semester)
	}

	\resumeitem{2016 -- 2017}{University of Queensland}{Summer Research Scholar}{		
		Worked with Professor Ian Hayes on extending \textbf{Java} to support interface-like Capabilities to enforce explicit permissions and restrict cross-object privilege access.
		
		Researched implementations of runtime interface dispatch and subtype checking, and began implementation of Capabilities in the \textbf{OpenJDK Parser / Compiler}.
	}

	\dateitem{2016}{\textbf{Google Summer of Code for The Julia Language}
		
		Developed an IDE-integrated interactive tutorial system for \textbf{Julia}. Presented at JuliaCon 2016.
	}
	
	\resumeitem{2014 -- 2016}{Tehnika Group}{Web Developer}{		
		Full stack web development and maintenance of large line--of--business web applications in \textbf{JavaScript} (\textbf{Node} and \textbf{Angular}), \textbf{PHP} and \textbf{C\# (ASP.NET)}.
	}
\end{itemize}

\resumesection{Skills}
\begin{itemize}[itemsep=1pt]
	\dateitem{Languages} {
%		Java, C\#, Julia, Python, HTML / CSS, SQL, JavaScript, C, Matlab, PHP
%		\textbf{Proficient:} Java, C\#, Julia, Python, HTML / CSS, SQL
%		
%		\textbf{Familiar:} JavaScript, C, Matlab, PHP

	\textit{Proficient:} Java, C\#, Julia, Python, HTML / CSS, SQL;
	\textit{Familiar:} JavaScript, C, Matlab, PHP
	}
	\dateitem{Technologies} {
		AWS, Spring, Git, Linux, \LaTeX
	}
%	\dateitem{Methodologies} {
%		Continuous Integration, Scrum, Kanban, Formal Verification
%	}
\end{itemize}

\resumesection{Awards}
\begin{itemize}[itemsep=1pt]
	\dateitem{2017 -- 2019} {\textbf{Hawken Scholar} Awarded to top 5\% of the UQ Engineering cohort.
	}
	\dateitem{2016 -- 2018} \textbf{Dean's Commendation for Academic Excellence}
	\dateitem{2016} {\textbf{Winner of UQ Computing Society Hackathon}
		
		For UQFlix, a \textbf{ASP.NET Core} web-app which streams video-on-demand from the UQ Library and offers recommendations using genre-based collaborative filtering machine learning in \textbf{Julia}.
	}
	\dateitem{2015} {\textbf{Paul Gampe Open Source Award at the UQ ITEE Excellence Showcase}
		
		For spearheading the open--sourcing of the FarmSim class project with over 60 contributors.
	}

	\dateitem{2015} {\textbf{QUT Hackathon Prize}
		
%		For the InCiteful web--app, which provides citation metrics for academics using Node.js and the Microsoft Academic Services API.
		
		An academic citation metrics web--app using \textbf{Node.js} and the Microsoft Academic Knowledge API.
		
%		For InCiteful, a Node.js web--app providing citation metrics for academics using the Microsoft Academic Knowledge API.
	}
	\dateitem{2013} {\textbf{Australian Student Prize} Awarded to the top 500 students nationally by the Education Minister.
	}
\end{itemize}

\resumesection{Projects}
\begin{itemize}	
	\dateitem{2016} {\textbf{Borealysis}
		
		Machine learning analysis of BHP borehole data at Unearthed Hackathon, achieving 90\% accuracy using \textbf{Deep Neural Networks} and \textbf{Nested Decision Forests} through \textbf{AzureML}.
	}
	
	\dateitem{2013} {\textbf{Evolutionary Image Compression Algorithm}
		
		\textbf{Genetic algorithm} in \textbf{C\#} for lossless image compression: up to 20\% smaller than zipped PNG.
	}
\end{itemize}

\bigskip
\end{document}
